The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
distmap_centroids corrections

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey
has detected \ncores\ clumps to a limiting depth of between
\bgpsdepthlow\ and \bgpsdepthhigh\ mJy RMS.  We include maps of 100
contiguous square degrees from $l=-10.5$ to $l=86.5$ and $b=\pm0.5$
with a resolution of 31\arcsec, as well as regions in IC1396, $l=111$
(NGC7538), W3/4/5, and Gem OB1.  The most striking feature of the maps
is the filamentary structure of cold dust throughout the Galaxy.

This paper details the survey observations and methods.  We treat
carefully the determination of pointing and flux density calibration errors
and compare our results to the literature.  Data processing algorithms
that separate astronomical signals from time-variable atmospheric flux density
in the data time-stream are discussed.  The algorithms reproduce the
structure of the astronomical sky on a limited range of angular scales
and produce artifacts in the vicinity of bright sources. Specifically,
extended emission smooth on scales larger than about 5\arcmin\ is not
fully recovered in the images.  The spatial frequency response
function of the Bolocam Galactic Plane Survey is discussed.

>>>>

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
the first large area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
$l=-10.5$ to $l=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
well as regions in IC1396, $l=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
striking feature of the maps is the filamentary structure of cold dust
throughout the Galaxy.

This paper details the survey observations and methods.  We treat carefully the
determination of pointing and flux density calibration errors and compare our
results to the literature.  Data processing algorithms that separate
astronomical signals from time-variable atmospheric flux density in the data
time-stream are discussed.  The algorithms reproduce the structure of the
astronomical sky on a limited range of angular scales and produce artifacts in
the vicinity of bright sources. Specifically, extended emission smooth on
scales larger than about 3\arcmin\ is not fully recovered in the images.  The
spatial frequency response function of the Bolocam Galactic Plane Survey is
discussed.
